---
title: "Raport danych"
author: "Gracjan"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

#Instalacja Pakietów

if (! require("tidyverse")) install.packages("tidyverse", dependencies = TRUE)
if (! require("dlookr")) install.packages("dlookr", dependencies = TRUE)
if (! require("VIM")) install.packages("VIM", dependencies = TRUE)
if (! require("validate")) install.packages("validate", dependencies = TRUE)
if (! require("editData")) install.packages("editData"), dependencies = TRUE)
if (! require("editrules")) install.packages("editrules"), dependencies = TRUE)

#Wczytywanie bibliotek

library(tidyverse)
library(dlookr)
library(VIM)
library(validate)
library(readr)
library(editData)
library(editrules)


#Wproadzenie danych

```{r}
Hipoteczny <- read_delim("Hipoteczny.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
hipo_baza <- Hipoteczny
```

#Wizualizacja Danych

```{r}
sum(is.na(hipo_baza))
hipo_baza <- hipo_baza[complete.cases(hipo_baza), ]
sum(is.na(hipo_baza))

```


#Czyszczenie Błedów

```{r}
sum(duplicated(hipo_baza$Loan_ID))
hipo_baza <- hipo_baza[!duplicated(hipo_baza$Loan_ID), ]
sum(duplicated(hipo_baza$Loan_ID))
hipo_baza <- hipo_baza[grepl("^LP\\d{6}$", hipo_baza$Loan_ID), ]  #czyszczenie jeśli nie mają LP i 6 cyfr
hipo_baza <- subset(hipo_baza, Gender %in% c("Male", "Female")) #czyszczenie jesli nie ma male lub female
hipo_baza <- subset(hipo_baza, Married %in% c("Yes", "No")) #czyszczenie jesli nie ma Yes lub No


```

#reguły
```{r}


   

```





