---
title: "Raport danych"
author: "Gracjan"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

#Instalacja Pakietów

if (! require("tidyverse")) install.packages("tidyverse", dependencies = TRUE)
if (! require("dlookr")) install.packages("dlookr", dependencies = TRUE)
if (! require("VIM")) install.packages("VIM", dependencies = TRUE)
if (! require("validate")) install.packages("validate", dependencies = TRUE)

#Wczytywanie bibliotek

<<<<<<< HEAD
library(tidyverse) library(dlookr) library(VIM) library(validate)

library(readr) Hipoteczny \<- read_delim("Hipoteczny.csv", delim = ";",
escape_double = FALSE, trim_ws = TRUE)
=======
library(tidyverse)
library(dlookr)
library(VIM)
library(validate)
library(readr)
>>>>>>> 6c31e8a1930a1c5d223277df8efb28d7c29fe3f2

#Wproadzenie danych

```{r}
Hipoteczny <- read_delim("Hipoteczny.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
hipo_baza <- Hipoteczny
```

#Wizualizacja Danych

```{r}
sum(is.na(hipo_baza))
hipo_baza <- hipo_baza[complete.cases(hipo_baza), ]
sum(is.na(hipo_baza))

```
